Universal Anonymous Signatures

### 2022-03-16 prism-backend/research/gsac/model-uas.tex
Updating model and generic construction.

We now define our model for Universal Anonymous Signatures. At a very high
level, it is a combination of the main models for group signatures and
anonymous credentials -- we try to extract the most useful features from both.
Instead of considering just one group, as in group signatures, we directly and
explicitly include support for multiple issuers as in anonymous credentials.
Moreover, instead of letting each user own a single credential, we allow
multiple credentials per user, even within the same group. This of course
makes us put forward refined notions of anonymity, traceability and
non-frameability. Note that, property-wise, we keep the three main properties
from group signatures, rather than sticking to the two usual properties of
anonymous credentials (anonymity and unforgeability). This is a consequence
of keeping the inspection capability from group signatures, which we consider
crucial in order to ensure some sort of accountability even in very adversarial
contexts where the issuer may be corrupt.
%
But, as stated in the introduction, we go beyond just combining anonymous
credentials and group signatures, and include support for arbitrary policies
during issuance, signing, and inspection. Consequently, our model needs to
capture the flexibility that these policies provide. In short, manipulations of
the issuance policy are only considered forgeries if the adversary manages to
create a valid signature using a credential that was obtained by dishonestly
manipulating the issuance policy (we discuss this further in the traceability
definition). Signing policies are taken into account both in the anonymity
property, where we need to restrict that both credentials used to produce the
challenge signatures always satisfy the policy, and in traceability.
\commentwho{Jesus}{Think a bit more about the following claim, and update if
  needed.}
We cannot give any assurance on the signing policies when the issuers are
corrupt, and thus they are not considered in the non-frameability property.
Inspection policies are considered both in traceability and non-frameability,
where the adversary wins if it manages to somehow alter the correct output of
\Inspect. What is even suprising, is that given the possible non-injectivity of
the inspection function lets us reach an even stronger notion of anonymity.
Namely, \uline{we can allow the adversary to open challenge signatures, as
  long as the inspection function outputs the same value for both}. We give more
details on these aspects in the actual definitions of the security properties.
%
Finally, from a functional perspective, we require that both issuer and
inspector fix the issuance predicate \fissue and inspection function \finsp when
generating their public keys. Indeed, both will be part of the common group key.
This also makes our definitions easier, as supporting multiple issuance
predicate and inspection functions per group would require to consider many
special cases -- and, anyway, that would probably end up being equivalent to
just requiring that a new group needs to be created per each $(\fissue,\$finsp)$
pair. On the other hand, signing policies can be defined at signing time (in
practice, most probably by the verifiers). This is in line with the usual
practice in anonymous credentials, that let users prove arbitrary claims on
their credentials, as long as they are met by the contained attributes.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace (\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\attrs$ plus, possibly, blinded attributes attested by
  previously obtained credentials $\cred_i$, from a multiset of other issuers
  (which may include the one to whom a new credential is being requested) with
  public keys $\gpk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.]
  The user with with secret key \usk and credential \cred, produces a signature
  \sig over message \msg, meeting the conditions defined by \feval.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Checks whether \sig is a valid
  signature, over message \msg, from a user in the group with public key \gpk.
\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg)$.] %
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg. If \trans contains a set of valid transcripts corresponding
  to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
  issued the used to produce \sig, the function outputs a value $\y$ derived
  from the signer's public key, credential, message, and signature, as well as
  a proof of correct inspection. We sometimes abuse notation, and write
  $\trans[\uid]$ to mean that the \Inspect function is operating only for the
  obtain transcripts related to user \uid.
\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials \scred, which may further be used for blind issuance
  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
  reject it.  
\item[$\feval: (\upk,\cred,\msg) \rightarrow 0/1$.] Can be defined by any party,
  although we anticipate that this will typically be done by either singers,
  verifiers, or some governance organization. It defines customized conditions
  to be met by the owner of a user key \upk and credential \cred, in
  order to sign a concrete message \msg. Returns $1$ to allow the signing,
  or $0$ to disallow it.
\item[$\finsp: (\upk,\cred,\msg) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credential, and message
  should be extractable by the group inspector.
\end{description}

@@

        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\cid,\sig,\msg,\feval)
          \in \SIG[\uid] \\
          (\y,\iproof) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
          \pcind (\y_{1-b},\iproof_{1-b}) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\\
          \hspace*{107pt} \trans,\sig_{1-b},\msg) \\
          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
          \pcreturn (\y,\iproof)
        }

@@

        \procedure{$\SIGN(\uid,\cid,\msg,\feval)$}{%
          \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid]) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\cid,\sig,\msg,\feval) \rbrace \\
          \pcreturn \sig \\
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced through a (set of)
credentials obtained by an honest user interacting with honest issuer(s), with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\cid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
    \pcif \Verify(\GK[\cid],\sig,\msg) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\cid) = 0: \pcreturn 1~
    \pccomment{\cid should not have been issued} \\
    \pcif \CorrectEval(\uid,\cid,\msg,\feval)
    = 0: \pcreturn 1~
    \pccomment{\msg should not have been signed}\\
    \pcif \CorrectInspect(\uid,\cid,\msg,\sig) = 0: \pcreturn 1~
    \pccomment{Some inspection of \sig is invalid}\\
    \pcreturn 0 \\
  }

@@

  \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
    \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
    \pcreturn 1 \\
  }

  \procedure{$\CorrectInspect(\uid,\cid,\msg,\sig)$}{
    \textrm{Let}~\gid \gets \GRP[\cid];~
    \textrm{Parse}~\GK[\gid]~\textrm{as}~(\cdot,(\cdot,\finsp^\gid)) \\
    \pccomment{\sig cannot be inspected} \\
    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) = \bot: \pcreturn 0 \\
    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
      % \todo{This must be conditioned on \feval = 0!}
    } \\
    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg)
    \land
    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0): \\
    \pcind \pcreturn 0 \\
    \pccomment{\y is the wrong value} \\
    \pcif \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\cid],\msg)):
    \pcreturn 0 \\
    \pcreturn 1
  }

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. Other than this, the overall approach is the same:
the adversary picks two honestly obtained credentials, and one of them (set
by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
oracle. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
\GEN,\lbrace\II,\OO\rbrace,\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$

@@

\begin{figure}[htp!]
    \procedure{$\ExpTrace(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\gid,\sig,\msg) \gets \adv^{\Otrace}(\parm) \\
      \pcif \Verify(\GK[\gid],\sig,\msg) = 0: \pcreturn 0 \\
      \pcif \EvalForge(\gid,\sig,\msg) = 1 \land
      \InspectForge(\gid,\sig,\msg) = 1: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0 \\
    }

    \procedure{$\EvalForge(\gid,\sig,\msg)$}{%
      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
      \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
      \pcind (\nexists \cred \in \CRED[\uid]~\st~
      \feval(\PUBUK[\uid],\cred,\msg) = 1 ~\lor \\
      \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
        fraudulently} \\
      \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
      \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
      \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
      \pcind \pcreturn 1 \\
      \pcelse \pcreturn 0 \\
    }

    \procedure{$\InspectForge(\gid,\sig,\msg)$}{%
      \pccomment{All \Obtain transcripts fail to inspect \sig} \\
      \pcif \Inspect(\PRVOK[\gid],\trans,\sig,\msg) \neq \bot~\lor \\
      \pcind \pccomment{A valid transcript exists, but ...} \\
      \pcind \exists \uid~\st~\Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg) =
      (\y,\iproof)~\land (\\
      \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0~\lor \\
      \pcind \pcind \pccomment{... or \uid does not own a \cred for which
        \finsp outputs \y} \\
      \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
      \y = \finsp(\PUBUK[\uid],\cred,\msg)~\lor \\
      \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
        fraudulently} \\
      \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
      \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
      \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
      \pcind \pcreturn 1 \\      
      \pcreturn 0
    }
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\gid,\sig,\msg,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg) = 1 \land
     \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
     \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
       from an honest \uid, owning a credential that makes \finsp
       evaluate to \y} \\
     \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
     (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
     \pcind \exists \cred \in \CRED[\uid]~\st~
     \finsp(\PUBUK[\uid],\cred,\msg) = \y \\
     \pccomment{\todo{I don't think we can give any assurance about \feval here,
         given that issuers are corrupt. But still, think about it.}} \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

We now define our model for Universal Anonymous Signatures. At a very high
level, it is a combination of the main models for group signatures and
anonymous credentials -- we try to extract the most useful features from both.
Instead of considering just one group, as in group signatures, we directly and
explicitly include support for multiple issuers as in anonymous credentials.
Moreover, instead of letting each user own a single credential, we allow
multiple credentials per user, even within the same group. This of course
makes us put forward refined notions of anonymity, traceability and
non-frameability. Note that, property-wise, we keep the three main properties
from group signatures, rather than sticking to the two usual properties of
anonymous credentials (anonymity and unforgeability). This is a consequence
of keeping the inspection capability from group signatures, which we consider
crucial in order to ensure some sort of accountability even in very adversarial
contexts where the issuer may be corrupt.
%
But, as stated in the introduction, we go beyond just combining anonymous
credentials and group signatures, and include support for arbitrary policies
during issuance, signing, and inspection. Consequently, our model needs to
capture the flexibility that these policies provide. In short, manipulations of
the issuance policy are only considered forgeries if the adversary manages to
create a valid signature using a credential that was obtained by dishonestly
manipulating the issuance policy (we discuss this further in the traceability
definition). Signing policies are taken into account both in the anonymity
property, where we need to restrict that both credentials used to produce the
challenge signatures always satisfy the policy, and in traceability.
\commentwho{Jesus}{Think a bit more about the following claim, and update if
  needed.}
We cannot give any assurance on the signing policies when the issuers are
corrupt, and thus they are not considered in the non-frameability property.
Inspection policies are considered both in traceability and non-frameability,
where the adversary wins if it manages to somehow alter the correct output of
\Inspect. What is even suprising, is that given the possible non-injectivity of
the inspection function lets us reach an even stronger notion of anonymity.
Namely, \uline{we can allow the adversary to open challenge signatures, as
  long as the inspection function outputs the same value for both}. We give more
details on these aspects in the actual definitions of the security properties.
%
Finally, from a functional perspective, we require that both issuer and
inspector fix the issuance predicate \fissue and inspection function \finsp when
generating their public keys. Indeed, both will be part of the common group key.
This also makes our definitions easier, as supporting multiple issuance
predicate and inspection functions per group would require to consider many
special cases -- and, anyway, that would probably end up being equivalent to
just requiring that a new group needs to be created per each $(\fissue,\finsp)$
pair. On the other hand, signing policies can be defined at signing time (in
practice, most probably by the verifiers). This is in line with the usual
practice in anonymous credentials, that let users prove arbitrary claims on
their credentials, as long as they are met by the contained attributes.

@@

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers). Hereafter, we assume that the
  public part \opk is added to the group public key \gpk, along with \finsp.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i) \rdblbrace_{i \in \Issuers})
  \rangle$.] %
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred from an issuer in the system, on
  attribute set $\attrs$ plus, possibly, blinded attributes attested by
  previously obtained credentials $\cred_i$, from a multiset of other issuers
  (which may include the one to whom a new credential is being requested) with
  public keys $\gpk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.]
  The user with with secret key \usk and credential \cred, produces a signature
  \sig over message \msg, meeting the conditions defined by \feval.
\item[$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.] Checks whether \sig is a
  valid signature, over message \msg, from a user in the group with public key
  \gpk, for signing function \feval.
\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.] %
  Executed by the inspector with private key \osk. Receives a signature \sig
  over message \msg and evaluation function \feval. If \trans contains a set of
  valid transcripts corresponding
  to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
  issued the credential used to produce \sig, the function outputs a value $\y$
  derived from the signer's public key, credential, message, and signature, as
  well as a proof of correct inspection. We sometimes abuse notation, and write
  $\trans[\uid]$ to mean that the \Inspect function is operating only for the
  obtain transcripts related to user \uid.
\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \y,
  obtained by applying \Inspect to the the signature \sig over message \msg. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
  governs what customized conditions an issuer requires in order to issue
  credentials, when receiving a request from user with public key \upk, for
  attributes \attrs. \fissue may run checks on a (possibly empty) set of
  additional credentials \scred, which may further be used for blind issuance
  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
  reject it.  
\item[$\feval: (\upk,\cred,\msg) \rightarrow \varrngfeval$.] Can be defined by any
  party, although we anticipate that this will typically be done by either
  signers, verifiers, or some governance organization. It defines customized
  conditions to be met by the owner of a user key \upk and credential \cred,
  in order to sign a concrete message \msg. Its outputs  $\varrngfeval$ must
  belong in a well defined set \rngfeval, with the restriction that it must
  return $0$ when the conditions for signing are not met.
\item[$\finsp: (\varrngfeval,\upk,\cred,\msg) \rightarrow \varrngfinsp$.]
  Defines what utility value, derived from the user's public key, credential,
  and message should be extractable by the group inspector. Note that \finsp
  also receives as input a value in the range of the \feval function, \rngfeval.
  This will allow inspection logic to depend on the value produced by the
  evaluation function. The output of \finsp is a value \varrngfinsp, which must
  belong in a well defined set \rngfinsp.
\end{description}

@@

        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\cid,\sig,\msg,\feval)
          \in \SIG[\uid] \\
          (\y,\iproof) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
          \pcind (\y_{1-b},\iproof_{1-b}) \gets
          \Inspect(\GK[\gid],\PRVOK[\gid],\\
          \hspace*{107pt} \trans,\sig_{1-b},\msg,\feval) \\
          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
          \pcreturn (\y,\iproof)
        }

@@

        \procedure{$\SIGN(\uid,\cid,\msg,\feval)$}{%
          \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid],\feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\cid,\sig,\msg,\feval) \rbrace \\
          \pcreturn \sig \\
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval \todo{Should we explicitly check \feval in the game?
  If so, how?},
produced honestly by an honest user \uid with credential \cid, is accepted by
\Verify. Moreover, upon issuance of the credential \cid, it must have met the
conditions set by \fissue. Similarly, the value returnd by \Inspect must be
accepted by \Judge, and must match the output of applying \finsp on \feval, the
credential, user key, and message.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\cid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
    \pcif \Verify(\GK[\cid],\sig,\msg,\feval) = 0: \pcreturn 1~
    \pccomment{\sig fails to verify} \\
    \pcif \CorrectIssue(\uid,\cid) = 0: \pcreturn 1~
    \pccomment{\cid should not have been issued} \\
    % \pcif \CorrectEval(\uid,\cid,\msg,\feval)
    % = 0: \pcreturn 1~
    % \pccomment{\msg should not have been signed} \\
    \pcif \CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval) = 0: \pcreturn 1~
    \pccomment{The combination of evaluation and inspection is wrong} \\
    \pcreturn 0 \\
  }

@@

  % \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
  %   \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
  %   \pcreturn 1 \\
  % }

  \procedure{$\CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval)$}{
    \textrm{Let}~\gid \gets \GRP[\cid];~
    \textrm{Parse}~\GK[\gid]~\textrm{as}~(\cdot,(\cdot,\finsp^\gid)) \\
    \pccomment{\sig cannot be inspected} \\
    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) = \bot: \pcreturn 0 \\
    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
      % \todo{This must be conditioned on \feval = 0!}
    } \\
    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval)
    \land
    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0: \\
    \pcind \pcreturn 0 \\
    \pccomment{\y is the wrong value} \\
    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\cid],\msg),
    \PUBUK[\uid],\CRED[\cid],\msg)):
    \pcreturn 0 \\
    \pcreturn 1
  }

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. Other than this, the overall approach is the same:
the adversary picks two honestly obtained credentials, and one of them (set
by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
oracle. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$

@@

\begin{figure}[htp!]
    \procedure{$\ExpTrace(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\gid,\sig,\msg,\feval) \gets \adv^{\Otrace}(\parm) \\
      \pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
      \pcif \EvalInspectForge(\gid,\sig,\msg,\feval) = 1 \\%\land
%      \InspectForge(\gid,\sig,\msg,\feval) = 1: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0 \\
    }

    % \procedure{$\EvalForge(\gid,\sig,\msg,\feval)$}{%
    %   \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
    %   \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
    %   \pcind (\nexists \cred \in \CRED[\uid]~\st~
    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0 ~\lor \\
    %   \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
    %     fraudulently} \\
    %   \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0~\land \\
    %   \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
    %   \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
    %     $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
    %   \pcind \pcreturn 1 \\
    %   \pcelse \pcreturn 0 \\
    % }

    \procedure{$\EvalInspectForge(\gid,\sig,\msg,\feval)$}{%
      \pccomment{All \Obtain transcripts fail to inspect \sig} \\
      \pcif \Inspect(\PRVOK[\gid],\trans,\sig,\msg) \neq \bot~\lor \\
      \pcind \pccomment{A valid transcript exists, but ...} \\
      \pcind \exists \uid~\st~\Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg) =
      (\y,\iproof)~\land (\\
      \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0~\lor \\
      \pcind \pcind \pccomment{... or \uid does not own a \cred for which
        \finsp outputs \y} \\
      \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
      \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
      \PUBUK[\uid],\cred,\msg)~\lor \\
      \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
        fraudulently} \\
      \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
      y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
      \PUBUK[\uid],\cred,\msg)~\land \\
      \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
      \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
      \pcind \pcreturn 1 \\      
      \pcreturn 0
    }
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\gid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 1 \land
     \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
     \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
       from an honest \uid, owning a credential that makes \finsp
       evaluate to \y} \\
     \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
     (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
     \pcind \exists \cred \in \CRED[\uid]~\st~
     \finsp(\feval(\PUBUK[\uid],\cred,\msg),\PUBUK[\uid],\cred,\msg) = \y \\
%     \pccomment{\todo{I don't think we can give any assurance about \feval here,
%         given that issuers are corrupt. But still, think about it.}} \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
